Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-02-08 manuscript/manuscript.Rmd
WIP

            #for(method in c("box_cox", "yeo_johnson")){
            for(method in c("yeo_johnson")){
              for(weight_method in c("none", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine")){

@@

                # Optimal parameter values from the previous experiment.
                if(weight_method == "original_cosine"){
                  k1 <- 0.89
                  k2 <- 0.93

@@

# Update distribution, method and version to factors.
data$distribution <- factor(
  x = data$distribution,
  levels = c("normal", "right-skewed", "left-skewed"))
data$method <- factor(
  x = data$method,
  levels = c("yeo_johnson"),
  labels = c("Yeo-Johnson"))
data$weight_method <- factor(
  x = data$weight_method,
  levels = c("none", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine"),
  labels = c("non-robust", "emp. prob. (tap. cos.)", "z-score (step)", "z-score (tap. cos.)", "residual (step)", "residual (tap. cos.)"))

@@

top_group <- c("non-robust", "emp. prob. (tap. cos.)", "z-score (step)")
bottom_group <- c("z-score (tap. cos.)", "residual (step)", "residual (tap. cos.)")

#### Normal distribution -------------------------------------------------------
p_normal_t <- .create_outlier_fraction_plot(
  data = data[distribution == "normal" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits= c(0.0, 2.0),
  lambda_target = data[distribution == "normal" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_normal_t <- p_normal_t + ggplot2::ggtitle(label="normal distribution")
p_normal_t <- p_normal_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank())

p_normal_b <- .create_outlier_fraction_plot(
  data = data[distribution == "normal" & weight_method %in% bottom_group],
  plot_theme = plot_theme,
  limits= c(-2.5,  4.0),
  lambda_target = data[distribution == "normal" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_normal_b <- p_normal_b + ggplot2::theme(
  axis.text.x = ggplot2::element_text(
    angle=60.0,
    hjust=1.0))

#### Right skewed distribution -------------------------------------------------
p_right_t <- .create_outlier_fraction_plot(
  data = data[distribution == "right-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits= c(0.0, 2.0),
  lambda_target = data[distribution == "right-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_right_t <- p_right_t + ggplot2::ggtitle(label="right-skewed distribution")
p_right_t <- p_right_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

p_right_b <- .create_outlier_fraction_plot(
  data = data[distribution == "right-skewed" & weight_method %in% bottom_group],
  plot_theme = plot_theme,
  limits= c(-2.5,  4.0),
  lambda_target = data[distribution == "right-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_right_b <- p_right_b + ggplot2::theme(
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_text(
    angle=60.0,
    hjust=1.0))

#### Left skewed distribution --------------------------------------------------
p_left_t <- .create_outlier_fraction_plot(
  data = data[distribution == "left-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits= c(0.0, 2.0),
  lambda_target = data[distribution == "left-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda,
  guide = TRUE)
p_left_t <- p_left_t + ggplot2::ggtitle(label="left-skewed distribution")
p_left_t <- p_left_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

p_left_b <- .create_outlier_fraction_plot(
  data = data[distribution == "left-skewed" & weight_method %in% bottom_group],
  plot_theme = plot_theme,
  limits= c(-2.5,  4.0),
  lambda_target = data[distribution == "left-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_left_b <- p_left_b + ggplot2::theme(
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_text(
    angle=60.0,
    hjust=1.0))

>>>>

            #for(method in c("box_cox", "yeo_johnson")){
            for(method in c("yeo_johnson")){
              for(weight_method in c("none", "original_step", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine")){

@@

                # Optimal parameter values from the previous experiment.
                if(weight_method == "original_step"){
                  k1 <- 0.92

                } else if(weight_method == "original_cosine"){
                  k1 <- 0.89
                  k2 <- 0.93

@@

# Update distribution, method and version to factors.
data$distribution <- factor(
  x = data$distribution,
  levels = c("normal", "right-skewed", "left-skewed"))
data$method <- factor(
  x = data$method,
  levels = c("yeo_johnson"),
  labels = c("Yeo-Johnson"))
data$weight_method <- factor(
  x = data$weight_method,
  levels = c("none", "original_step", "original_cosine", "transformed_step", "transformed_cosine", "residual_step", "residual_cosine"),
  labels = c("non-robust", "emp. prob. (step)", "emp. prob. (tap. cos.)", "z-score (step)", "z-score (tap. cos.)", "residual (step)", "residual (tap. cos.)"))

@@

top_group <- c("non-robust", "emp. prob. (step)", "emp. prob. (tap. cos.)")
bottom_group <- c("z-score (step)", "z-score (tap. cos.)", "residual (step)", "residual (tap. cos.)")

top_limits <- c(0.2, 1.8)
bottom_limits <- c(-2.5, 4.0)

#### Normal distribution -------------------------------------------------------
p_normal_t <- .create_outlier_fraction_plot(
  data = data[distribution == "normal" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits = top_limits,
  lambda_target = data[distribution == "normal" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_normal_t <- p_normal_t + ggplot2::ggtitle(label="normal distribution")
p_normal_t <- p_normal_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank())

p_normal_b <- .create_outlier_fraction_plot(
  data = data[distribution == "normal" & weight_method %in% bottom_group],
  plot_theme = plot_theme,
  limits = bottom_limits,
  lambda_target = data[distribution == "normal" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_normal_b <- p_normal_b + ggplot2::theme(
  axis.text.x = ggplot2::element_text(
    angle=60.0,
    hjust=1.0))

#### Right skewed distribution -------------------------------------------------
p_right_t <- .create_outlier_fraction_plot(
  data = data[distribution == "right-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits= top_limits,
  lambda_target = data[distribution == "right-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_right_t <- p_right_t + ggplot2::ggtitle(label="right-skewed distribution")
p_right_t <- p_right_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

p_right_b <- .create_outlier_fraction_plot(
  data = data[distribution == "right-skewed" & weight_method %in% bottom_group],
  plot_theme = plot_theme,
  limits = bottom_limits,
  lambda_target = data[distribution == "right-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_right_b <- p_right_b + ggplot2::theme(
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_text(
    angle=60.0,
    hjust=1.0))

#### Left skewed distribution --------------------------------------------------
p_left_t <- .create_outlier_fraction_plot(
  data = data[distribution == "left-skewed" & weight_method %in% top_group],
  plot_theme = plot_theme,
  limits = top_limits,
  lambda_target = data[distribution == "left-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda,
  guide = TRUE)
p_left_t <- p_left_t + ggplot2::ggtitle(label="left-skewed distribution")
p_left_t <- p_left_t + ggplot2::theme(
  axis.title.x = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_blank(),
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

p_left_b <- .create_outlier_fraction_plot(
  data = data[distribution == "left-skewed" & weight_method %in% bottom_group],
  plot_theme = plot_theme,
  limits = bottom_limits,
  lambda_target = data[distribution == "left-skewed" & weight_method == "non-robust" & k == 0.0]$mean_lambda)
p_left_b <- p_left_b + ggplot2::theme(
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank(),
  axis.text.x = ggplot2::element_text(
    angle=60.0,
    hjust=1.0))
